Consumer Reviews and Product Discounts:\\ Evidence From Video Games

### 2020-08-08 Analysis/Output/Paper.tex
Initial commit.

---
 title: |
   | Consumer Reviews and Product Discounts:
   | Evidence From Video Games

 author: "Dmitry Sorokin"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
 classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
 output:
  pdf_document:
    keep_tex: true
    fig_height: 2.5
    fig_width: 6
    number_sections: true
    citation_package: natbib
    extra_dependencies:
       footmisc: ["bottom"] # footnote management
       setspace: ["doublespacing"] # spacing of the paper
       caption: ["tableposition=top"]
       dsfont: null # indicator function 1
       booktabs: null
       makecell: null
    includes:
       in_header: extra_header.tex

 bibliography: reviewsBib.bib
 fontsize: 12pt
 geometry: margin=1in
 link-citations: true
 linkcolor: mypink
 filecolor: myblue
 citecolor: mypink
 urlcolor: mypink
---

```{r cache = F}
source(here("Analysis", "Code", "StructuralFunctions.R"))
load(here("Analysis", "Input", "info.Rda"))
load(here("Analysis", "Input", "panel.Rda"))
```

# Introduction

# Literature Review

This paper contributes to several closely related literatures in economics and marketing. The oldest of these is the literature investigating the impact of online consumer reviews on sales. An extensive review of the studies focusing on this topic and their meta-analysis is provided, for example, by @Floyd14. 
<!-- Researchers have analyzed multiple online platforms, selling different products and employing different review systems, and produced, overall, conflicting evidence on whether reviews improve sales, and if so, through which channels. The major identification challenge stems from the fact that better reviews might simply be manifestations of consumer preferences for certain products, or reflect higher quality of the underlying products. As preferences and quality are unobserved and, in general, fluid, researchers have struggled to come up with convincing identification strategies. -->
In a seminal contribution in this literature, @ChevalierMayzlin06 uses a difference-in-differences approach, exploiting the differences in reviews for the same books across Amazon.com and Barnesandnoble.com, to argue that better reviews causally improve sales. A similar approach applied to the same market was recently used by @ReimersWaldfogel20, who reaffirm the importance of reviews for sales of books and quantify the welfare implications of the informational content of consumer reviews. @ZhuZhang10 exploit differences between two different video games consoles rather than websites, and find that review ratings matter only for less popular games.

For identification, the difference-in-differences approach relies on the existence of several comparable platforms, and assumes that the unobserved platform-specific tastes
for those platforms are fixed. Another approach to identification exploits the rounding of the review data that platforms use to produce simple visual review labels. For example, Yelp.com, a popular restaurant comparison service, assigns 4 stars to restaurants that have an average review score between 4 and 4.24 (out of 5), but 4.5 stars to restaurants with an average score between 4.25 and 4.74.  @AndersonMagruder12 and @Luca16 develop a regression discontinuity approach exploiting this rounding to show that an additional half-star on Yelp.com increases restaurants' traffic and revenue. @SorokinStevens20 applies a similar approach to the video games market and also finds that better review labels increase sales, albeit raising some concerns about the validity of the approach. In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from the video games' usage data. The present paper supplements the panel methods in @SorokinStevens20 by offering a structural way to estimate the effect of reviews on sales in the absence of direct sales data.

With benefits of having good reviews come the incentives to influence the reviews in order to reap those benefits. There are several ways firms can affect their online reviews. One is review fraud. @Mayzlin14 provides evidence that small hotel owners leave negative reviews for their competitors, and good reviews for themselves. @LucaZervas16 provide similar evidence for restaurants on Yelp. A more honest way for a firm to influence reviews is by assuming an active approach to review management, and to publicly respond to reviews published online. @GuYe14 provide evidence that consumers who had left a negative review about their hotel experience in the past were more likely to leave a positive review of the same hotel after a future stay if their previous review was responded to by the management. @XieEtAl17 shows that lengthy in-depth managerial responses to negative reviews are associated with better financial performance in the future. This literature has also been concerned with how consumers change their reviewing behavior when managers start responding to reviews, essentially moving from studying individual responses to describing equilibrium outcomes. In somewhat contradictory findings, @ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the valence and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they can be responded to, while @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage negative review activity, because consumers get a signal that the firm is “listening” to them, and are then stimulated to leave negative reviews that they deem more influential.

Direct ways of managing online reputation discussed above, however, are not the only avenues through which businesses can affect their reviews. Reviews are left by customers, and the happier they are, the better reviews they should leave, at least in principle. Another strand of literature is studying whether different kinds of promotions have an effect on firms' online reputation. In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a Groupon price promotion. They present evidence that customers attracted by the promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher, which can explain the reasons behind their dissatisfaction. Thus, the paper cautions against running price promotions in an attempt to poach new customers and improve the online reputation. @Li16 confirms the finding in the same setting, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion. @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews. In an experimental study on Ebay, @CabralLi15 also find that offering a rebate for leaving (any) review significantly decreased the likelihood of negative feedback, and they provide evidence that this is due to reciprocity on the side of the clients, rather than the differences between customers buying with a rebate and without it.

The present study contributes to this literature by providing novel evidence from a new market. I show that customers buying computer games are significantly more likely to leave positive reviews during discounts. More importantly, I go beyond the descriptive nature of the other papers in the literature, and show that firms leverage this fact to improve their reviews by giving discounts, thus providing evidence of a novel reputation management behavior. A study similar in spirit to mine is that of @Zegners17, who argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap". However, this study also finds that books are more likely to solicit negative feedback when sold for free, which somewhat undermines the strategy. Similar to @ByersEtAl12, @Zegners17 argues that purchasers of free books differ from the purchasers of regular books in their observable characteristics, and explains the negativity of the reviews by the selection effect.

# Institutional Setting and Data

## Steam Marketplace

Steam is arguably the largest online marketplace for selling computer games in the world. Founded in 2003, in 2013 it was responsible for about 75\% of PC games sold online globally [@steamBloomberg], and in 2017 it has earned around US\$4.3 billion, with an estimated market share of 18\% in the entire market for PC games [@psgames]. Given an ongoing unprecedented growth in the size of the video games' market [\$43.4 billion 
in 2018, about the size of the U.S. film industry, @videoGamesMarket] and the increasing share of online sales in this market [83\% in 2018, compared to 20\% in 2009, @steamNPD], Steam is a major player in an increasingly more important industry. Thus, this marketplace is not merely a laboratory for studies hoping to extrapolate the findings to other more well-known platforms, but is an important digital market to be studied in its own right.

Any user who has a copy of a game on Steam can leave a review for that game. Starting from late 2016, by default, Steam only uses reviews left by customers who have *purchased* the game in its review score calculation, excluding reviews left by customers who had obtained a key to activate the game through other channels (directly from the developer, or by purchasing the code from a different retailer). This distinguishes Steam from some other platforms studied in the literature, notably Yelp and TripAdvisor, where any user can leave a review (and, to a certain extent, Amazon, where non-verified users can also leave reviews). This gives me confidence in the authenticity of most reviews. This confidence is further backed by the importance of Steam to game developers and publishers, and Steam's history of monitoring the platform for fraudulent activity and excluding unscrupulous actors. With such high stakes, and a non-negligible risk of being caught, there are good reasons to expect the developers to behave scrupulously.

A review consists of a binary grade, "thumbs up" or "thumbs down", and review's text. A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews. Based on the score, Steam assigns *review labels*, or bins, to each game. These labels\footnote{There are labels worse than "Negative", but they are rare, so I bin all of them into "Negative"} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}. For example, a game with 7 positive and 2 negative reviews would have neither a review score, nor a label, but an extra positive review would promote it to the “Positive” bin.

```{r}
tab <- data.table(`Review Bin` = c("No Score", "Negative", "Mixed", "Mostly Positive", 
                                   "Positive", "Very Positive", "Overwhelmingly Positive"),
                  `N. of Reviews` = c("[0, 10)", "Any", "Any", "Any", "[0, 50)", 
                                          "More than 50", "More than 500"),
                  `Score` = c("-", "[0, 40)", "[40, 70)", "[70, 80)", "[80, 100)",
                              "[80, 100)", "[95, 100]"))
kable(tab, "latex",
      label = "ReviewBinsTable",
      caption = "The mapping between the review score and review bins on Steam",
      align = c('l', "c", "c"),
      valign = 't',
      linesep = "",
      booktabs = T)
```

Steam's homepage welcomes customers with a selection of featured games, that could include new games, popular games that are currently on a discount, games that have recently released a major update, etc. [@steamVisibility]. A customer could either click on the games already presented to her, or browse one of the categories that Steam offers. Available categories are based on games' characteristics such as performance (e.g., “Top Sellers”, “New Releases”), genre (e.g, “Racing”, "Anime", “Simulation”), or technical characteristics (VR or controller support). Games within a category are organized into a list, with an example session presented in Figure \ref{steamStore}. From that list the user can get some basic information about each game, such as its name, price, and if the game is currently on a discount. Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has. I use this feature of the Steam's store to rationalize why later in the analysis I choose to focus on the review labels as my main independent review variables, rather than, say, the review score or the review texts. Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place. Thus, I conjecture that games with better review labels will, other things equal, attract more customers, and lead to more sales. Crucially, according to Steam's documentation, all review labels better than “Negative“ have a very similar contribution to visibility on the platform, which means, for example, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2]. Therefore, any effect of the review labels on, say sales, should come through the perceived quality differences between different bins, rather than some mechanical visibility differences. As an illustration, note that the first game in the list depicted in Figure \ref{steamStore} has “Mixed” reviews.

 ```{r fig.cap='\\label{steamStore}Example Browsing Session on Steam', out.width="75%", fig.align="center"}
 knitr::include_graphics(here("Analysis", "Output", "Paper_files", "figure-latex", "steamStore.pdf"))
 ```

## Data

Valve Corporation, the owner of Steam, is notoriously secretive about its data and algorithms. Given the importance of the information on the performance of different games for game developers and publishers, the community has responded to this secrecy by establishing projects that monitor Steam in real time and extract  information that could be relevant for parties interested in Steam. The majority of data used in this project comes from one such project called “Steam Database”, or “SteamDB”.

Descriptive information on any game, that I will refer to as “static”, such as its title, developer, release date, etc., are readily available from Steam, and this information is also present on SteamDB. More importantly, Steam Database offers a daily time series of prices and player activity for each game on Steam. In principle, the pricing information could be obtained by a repeated scraping of the store. However, the player activity information is not trivial to obtain, as Steam does not directly reveal such data, let alone the data on sales of different titles. The creators of SteamDB have declined to explain their collection method, but their reputation in the gaming community most certainly implies that they are doing the best they can. The resulting variable that SteamDB offers, that I will refer to as the *player count*, measures the maximum number of concurrent player for each game on a daily basis. In other words, if on a particular day 10 people play the game every hour, except noon, when 13 people play the game simultaneously, then the recorded player count for this game on that day will be 13. The price and the player count time series are the major “dynamic” variables used in the analysis. The last dynamic variable, namely the evolution of the review score for each game, is obtained by scraping the reviews directly from Steam, and reverse engineering the path of the review score.

```{r example-game, fig.cap='\\label{exampleGame} An Example Game in the Sample: Player Count, Price, and Review Score Histories.', fig.height = 5}
plotGame(589530)
```

Steam is home to more than 25,000 games that differ in their genres, prices, sales, release dates, frequency of updates, and other characteristics. Inevitably, an appropriate sample should be selected for the analysis. @SorokinStevens20 studies the causal effect of reviews on sales on Steam, and I mirror closely the sample selection procedure used in that paper. First, Steam has made some significant changes to its review system in late 2016, and one of the effects was the removal of the a big number of reviews from the review score calculation. While it could be an intervention that is worthy of an independent study, in practice combining the data from before and after the intervention led to unsound results, so I focus on the two year period from January 2017 to January 2019, keeping the review system as stable as possible. In particular, only games that were released in this time period make it to the sample.

Second, online multiplayer games and games that update frequently are dropped from the sample, as these are products whose quality is changing a lot over time\footnote{Games on Steam have blogs that allow them to share news about updates with the audience. Publishing news about an update is voluntary, so it is possible that some games that continue to update after the release still made it to the sample.}. Unobserved quality would present a big obstacle to the identification of the effect of reviews on pricing decisions or sales, because, say, a game that has just issued a major update might both upgrade to a better review label (because of the positive reception of the new content) and give a big discount to rekindle the interest of the players, but the discounting decision would not be influenced by the review transition. For the same reasons, I also drop free games and games that are released in a beta-version (the so called “Early Access” program), as these products are likely to be adding new content, and the update history is not a perfect way to monitor the updating activity. Finally, I drop few games with a player count of less than four on their median day, as these games are simply very small, and the quality of their player count data is questionable.

## Sample Description

The final sample includes `r info[, .N]` games which I observe for `r panel[, max(age), by = ID][, round(mean(V1))]` days each, on average. The main variables in the analysis are the aforementioned dynamic variables: player count, price, and review score history. An example observation from the sample is given in Figure \ref{exampleGame}. For the majority of the games in the sample, the player count is the highest around the release date, and then it quickly fades away and oscillates around a smaller level. The player count also jumps when a discount is given, reflecting the influx of new players. Games differ a lot in their sizes, as is evident from Figure \ref{sampleSizeHist}.

```{r sample-size-hist, fig.cap='\\label{sampleSizeHist} Distributions of the Player Count on, and the Number of Reviews Accumulated by, the Age of 180 Days.'}
p1 <- ggplot(data = panel[age==180, .(x = log(number))]) +
  geom_histogram(mapping = aes(x = x, y = ..density..), 
                 color = "black", 
                 position = "identity", 
                 alpha = 0.9,
                 binwidth = 0.5,
                 boundary = 0,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x), 
                 color = "black", 
                 position = "identity", 
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Log Players",
                     breaks = seq(0, 8),
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL, 
                     minor_breaks = NULL) +
  my.theme()

p2 <- ggplot(data = panel[age==180, .(x = log(reviews))]) +
  geom_histogram(mapping = aes(x = x, y = ..density..), 
                 color = "black", 
                 position = "identity", 
                 alpha = 0.9,
                 binwidth = 0.5,
                 boundary = 0,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x), 
                 color = "black", 
                 position = "identity", 
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Log Reviews",
                     breaks = seq(0, 8),
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL, 
                     minor_breaks = NULL) +
  my.theme()

ggarrange(p1, p2, ncol = 2, nrow = 1, align = "h")
```

```{r sample-size-hist-vert, include=FALSE}
# for beamer
ggarrange(p1, p2, ncol = 1, nrow = 2, align = "h")
```

As the goal of the paper is to understand if firms use pricing tools in order to improve their online reputation, a detailed overview of pricing and review variables is important. A representative game in the sample never changes its price, but instead occasionally goes on discounts, slowly increasing their magnitude as the game ages. There are
`r panel[discount==F, diff(price), by = ID][V1>0, .N]` incidents of price change in the data, compared to 
`r panel[discNew==T, .N]` discounts. Steam has a number of rules that regulate price promotions on its platform. A game can have a launch discount, but, otherwise, it has to wait for two months since the release before changing its price or giving a discount. A game can not go on discounts too frequently, and has to wait between four to six weeks
after a price promotion to be able to run a new one. The duration of a custom discount is restricted to be at least one full day, and at most two weeks. Besides these custom discounts, that are fully managed by the firms, Steam has a series of curated discounts, when the platform invites selected titles to go on a discount. As @steamDiscounting explains it, “while there aren't strict rules, as a base guideline we tend to focus on the top 10-20% selling games on Steam that are positively reviewed and have otherwise proven to be successful”. Curated promotions are featured prominently on Steam's main page, and, arguably, lead to more visibility and sales for the participating titles than custom discounts, which also contribute to visibility, but typically do not get the front-page promotional slots. An important type of curated discounts are the so-called “Seasonal Sales”--big platform-wide events that take place about four times a year around major holidays. Figure \ref{seasonalSales} shows that the biggest sales take place in Winter (Christmas and New Year) and Summer (July 4), but there are also significant discounts in the Fall (Halloween and Thanksgiving). Around `r  round(panel[discSeason==T & discNew == T, .N]/panel[discNew==T, .N]*100)`% of discounts in the sample go live during a Seasonal Sale. Thus, firms have significant agency when it comes to running price promotions, but platform regulations and platform-wide discounts are important determinants of firms' decision to discount.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
  12pt,
  pagebackref]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdfauthor={Dmitry Sorokin},
  colorlinks=true,
  linkcolor=mypink,
  filecolor=myblue,
  citecolor=mypink,
  urlcolor=mypink,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\renewcommand{\ttdefault}{cmr} % change the font of inline R results to normal
\renewcommand*{\backref}[1]{}
\renewcommand*{\backrefalt}[4]{%
    \ifcase #1 (Not cited.)%
    \or        [Cited on page~#2.]%
    \else      [Cited on pages~#2.]%
    \fi}
\setlength{\parindent}{25pt}
\setlength{\parskip}{0pt}
\setlength{\skip\footins}{0.25cm} % margin before footnotes
\definecolor{myblue}{RGB}{31, 61, 122}
\definecolor{mypink}{RGB}{204, 0, 82}
\newtheorem{assumption}{Assumption}[section]
\newtheorem{proposition}{Proposition}[section]
\newcommand{\EE}[1]{\mathbb{E}\left[#1\right]}
\newcommand{\PP}[1]{\mathbb{P}\left(#1\right)}
\newcommand{\CP}[2]{\mathbb{P}\left(#1 \,| \, #2 \right)}
\newcommand{\CE}[2]{\mathbb{E}\left[#1\,|\,#2 \right]}
\usepackage[bottom]{footmisc}
\usepackage[doublespacing]{setspace}
\usepackage[tableposition=top]{caption}
\usepackage{dsfont}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\title{Consumer Reviews and Product Discounts:\\
Evidence From Video Games}
\author{Dmitry Sorokin}
\date{August 08, 2020}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{literature-review}{%
\section{Literature Review}\label{literature-review}}

This paper contributes to several closely related literatures in
economics and marketing. The oldest of these is the literature
investigating the impact of online consumer reviews on sales. An
extensive review of the studies focusing on this topic and their
meta-analysis is provided, for example, by \citet{Floyd14}. In a seminal
contribution in this literature, \citet{ChevalierMayzlin06} uses a
difference-in-differences approach, exploiting the differences in
reviews for the same books across Amazon.com and Barnesandnoble.com, to
argue that better reviews causally improve sales. A similar approach
applied to the same market was recently used by
\citet{ReimersWaldfogel20}, who reaffirm the importance of reviews for
sales of books and quantify the welfare implications of the
informational content of consumer reviews. \citet{ZhuZhang10} exploit
differences between two different video games consoles rather than
websites, and find that review ratings matter only for less popular
games.

For identification, the difference-in-differences approach relies on the
existence of several comparable platforms, and assumes that the
unobserved platform-specific tastes for those platforms are fixed.
Another approach to identification exploits the rounding of the review
data that platforms use to produce simple visual review labels. For
example, Yelp.com, a popular restaurant comparison service, assigns 4
stars to restaurants that have an average review score between 4 and
4.24 (out of 5), but 4.5 stars to restaurants with an average score
between 4.25 and 4.74. \citet{AndersonMagruder12} and \citet{Luca16}
develop a regression discontinuity approach exploiting this rounding to
show that an additional half-star on Yelp.com increases restaurants'
traffic and revenue. \citet{SorokinStevens20} applies a similar approach
to the video games market and also finds that better review labels
increase sales, albeit raising some concerns about the validity of the
approach. In the absence of direct sales data, \citet{SorokinStevens20}
uses a particular regression specification that extracts the information
on sales from the video games' usage data. The present paper supplements
the panel methods in \citet{SorokinStevens20} by offering a structural
way to estimate the effect of reviews on sales in the absence of direct
sales data.

With benefits of having good reviews come the incentives to influence
the reviews in order to reap those benefits. There are several ways
firms can affect their online reviews. One is review fraud.
\citet{Mayzlin14} provides evidence that small hotel owners leave
negative reviews for their competitors, and good reviews for themselves.
\citet{LucaZervas16} provide similar evidence for restaurants on Yelp. A
more honest way for a firm to influence reviews is by assuming an active
approach to review management, and to publicly respond to reviews
published online. \citet{GuYe14} provide evidence that consumers who had
left a negative review about their hotel experience in the past were
more likely to leave a positive review of the same hotel after a future
stay if their previous review was responded to by the management.
\citet{XieEtAl17} shows that lengthy in-depth managerial responses to
negative reviews are associated with better financial performance in the
future. This literature has also been concerned with how consumers
change their reviewing behavior when managers start responding to
reviews, essentially moving from studying individual responses to
describing equilibrium outcomes. In somewhat contradictory findings,
\citet{ProserpioZervas17} argues that hotels responding to bad reviews
experience an increase in both the valence and the volume of their
reviews, attributing it to consumers' reluctance to leave short
indefensible reviews in a situation when they can be responded to, while
\citet{ChevalierEtAl18} finds the opposite effect in the same market,
arguing that managerial responses encourage negative review activity,
because consumers get a signal that the firm is ``listening'' to them,
and are then stimulated to leave negative reviews that they deem more
influential.

Direct ways of managing online reputation discussed above, however, are
not the only avenues through which businesses can affect their reviews.
Reviews are left by customers, and the happier they are, the better
reviews they should leave, at least in principle. Another strand of
literature is studying whether different kinds of promotions have an
effect on firms' online reputation. In a seminal study,
\citet{ByersEtAl12} documents that restaurants receive substantially
worse reviews after running a Groupon price promotion. They present
evidence that customers attracted by the promotion are different from
regular customers, and that they are more likely to be trying out a new
restaurant or cuisine while using the Groupon voucher, which can explain
the reasons behind their dissatisfaction. Thus, the paper cautions
against running price promotions in an attempt to poach new customers
and improve the online reputation. \citet{Li16} confirms the finding in
the same setting, but finds that restaurants with fewer and worse
reviews can actually benefit from participating in a Groupon promotion.
\citet{ZhuEtAl19} shows that customers who received a discount leave
more positive, albeit less informative, reviews. In an experimental
study on Ebay, \citet{CabralLi15} also find that offering a rebate for
leaving (any) review significantly decreased the likelihood of negative
feedback, and they provide evidence that this is due to reciprocity on
the side of the clients, rather than the differences between customers
buying with a rebate and without it.

The present study contributes to this literature by providing novel
evidence from a new market. I show that customers buying computer games
are significantly more likely to leave positive reviews during
discounts. More importantly, I go beyond the descriptive nature of the
other papers in the literature, and show that firms leverage this fact
to improve their reviews by giving discounts, thus providing evidence of
a novel reputation management behavior. A study similar in spirit to
mine is that of \citet{Zegners17}, who argues that less-known authors of
eBooks on a crowded online marketplace are more likely to give their
books out for free in order to build reputation and escape the ``zero
reviews trap''. However, this study also finds that books are more
likely to solicit negative feedback when sold for free, which somewhat
undermines the strategy. Similar to \citet{ByersEtAl12},
\citet{Zegners17} argues that purchasers of free books differ from the
purchasers of regular books in their observable characteristics, and
explains the negativity of the reviews by the selection effect.

\hypertarget{institutional-setting-and-data}{%
\section{Institutional Setting and
Data}\label{institutional-setting-and-data}}

\hypertarget{steam-marketplace}{%
\subsection{Steam Marketplace}\label{steam-marketplace}}

Steam is arguably the largest online marketplace for selling computer
games in the world. Founded in 2003, in 2013 it was responsible for
about 75\% of PC games sold online globally \citep{steamBloomberg}, and
in 2017 it has earned around US\$4.3 billion, with an estimated market
share of 18\% in the entire market for PC games \citep{psgames}. Given
an ongoing unprecedented growth in the size of the video games' market
\citep[\$43.4 billion in 2018, about the size of the U.S. film
industry,][]{videoGamesMarket} and the increasing share of online sales
in this market \citep[83\% in 2018, compared to 20\% in
2009,][]{steamNPD}, Steam is a major player in an increasingly more
important industry. Thus, this marketplace is not merely a laboratory
for studies hoping to extrapolate the findings to other more well-known
platforms, but is an important digital market to be studied in its own
right.

Any user who has a copy of a game on Steam can leave a review for that
game. Starting from late 2016, by default, Steam only uses reviews left
by customers who have \emph{purchased} the game in its review score
calculation, excluding reviews left by customers who had obtained a key
to activate the game through other channels (directly from the
developer, or by purchasing the code from a different retailer). This
distinguishes Steam from some other platforms studied in the literature,
notably Yelp and TripAdvisor, where any user can leave a review (and, to
a certain extent, Amazon, where non-verified users can also leave
reviews). This gives me confidence in the authenticity of most reviews.
This confidence is further backed by the importance of Steam to game
developers and publishers, and Steam's history of monitoring the
platform for fraudulent activity and excluding unscrupulous actors. With
such high stakes, and a non-negligible risk of being caught, there are
good reasons to expect the developers to behave scrupulously.

A review consists of a binary grade, ``thumbs up'' or ``thumbs down'',
and review's text. A \emph{review score} is defined as the fraction of
positive reviews among all reviews a game has, provided it has at least
10 reviews. Based on the score, Steam assigns \emph{review labels}, or
bins, to each game. These
labels\footnote{There are labels worse than "Negative", but they are rare, so I bin all of them into "Negative"}
and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}.
For example, a game with 7 positive and 2 negative reviews would have
neither a review score, nor a label, but an extra positive review would
promote it to the ``Positive'' bin.

\begin{table}[t]

\caption{\label{tab:ReviewBinsTable}The mapping between the review score and review bins on Steam}
\centering
\begin{tabular}{lcc}
\toprule
Review Bin & N. of Reviews & Score\\
\midrule
No Score & [0, 10) & -\\
Negative & Any & [0, 40)\\
Mixed & Any & [40, 70)\\
Mostly Positive & Any & [70, 80)\\
Positive & [0, 50) & [80, 100)\\
Very Positive & More than 50 & [80, 100)\\
Overwhelmingly Positive & More than 500 & [95, 100]\\
\bottomrule
\end{tabular}
\end{table}

Steam's homepage welcomes customers with a selection of featured games,
that could include new games, popular games that are currently on a
discount, games that have recently released a major update, etc.
\citep{steamVisibility}. A customer could either click on the games
already presented to her, or browse one of the categories that Steam
offers. Available categories are based on games' characteristics such as
performance (e.g., ``Top Sellers'', ``New Releases''), genre (e.g,
``Racing'', ``Anime'', ``Simulation''), or technical characteristics (VR
or controller support). Games within a category are organized into a
list, with an example session presented in Figure \ref{steamStore}. From
that list the user can get some basic information about each game, such
as its name, price, and if the game is currently on a discount.
Importantly, if the user hovers her cursor over a game, she could
further see the review label of the game and the number of reviews the
game has. I use this feature of the Steam's store to rationalize why
later in the analysis I choose to focus on the review labels as my main
independent review variables, rather than, say, the review score or the
review texts. Granted, informative review texts could be important for
purchase decisions \citep{ChevalierMayzlin06}, but on Steam, in order to
gain access to such information, a customer should be willing to click
on the game in the first place. Thus, I conjecture that games with
better review labels will, other things equal, attract more customers,
and lead to more sales. Crucially, according to Steam's documentation,
all review labels better than ``Negative`` have a very similar
contribution to visibility on the platform, which means, for example,
that games are not ordered by their review labels when the customer is
browsing different categories \citeyearpar{steamVisibility2}. Therefore,
any effect of the review labels on, say sales, should come through the
perceived quality differences between different bins, rather than some
mechanical visibility differences. As an illustration, note that the
first game in the list depicted in Figure \ref{steamStore} has ``Mixed''
reviews.

\begin{figure}[h]

 {\centering \includegraphics[width=0.75\linewidth,]{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/steamStore}

 }

 \caption{\label{steamStore}Example Browsing Session on Steam}\label{fig:unnamed-chunk-3}
 \end{figure}

\hypertarget{data}{%
\subsection{Data}\label{data}}

Valve Corporation, the owner of Steam, is notoriously secretive about
its data and algorithms. Given the importance of the information on the
performance of different games for game developers and publishers, the
community has responded to this secrecy by establishing projects that
monitor Steam in real time and extract information that could be
relevant for parties interested in Steam. The majority of data used in
this project comes from one such project called ``Steam Database'', or
``SteamDB''.

Descriptive information on any game, that I will refer to as ``static'',
such as its title, developer, release date, etc., are readily available
from Steam, and this information is also present on SteamDB. More
importantly, Steam Database offers a daily time series of prices and
player activity for each game on Steam. In principle, the pricing
information could be obtained by a repeated scraping of the store.
However, the player activity information is not trivial to obtain, as
Steam does not directly reveal such data, let alone the data on sales of
different titles. The creators of SteamDB have declined to explain their
collection method, but their reputation in the gaming community most
certainly implies that they are doing the best they can. The resulting
variable that SteamDB offers, that I will refer to as the \emph{player
count}, measures the maximum number of concurrent player for each game
on a daily basis. In other words, if on a particular day 10 people play
the game every hour, except noon, when 13 people play the game
simultaneously, then the recorded player count for this game on that day
will be 13. The price and the player count time series are the major
``dynamic'' variables used in the analysis. The last dynamic variable,
namely the evolution of the review score for each game, is obtained by
scraping the reviews directly from Steam, and reverse engineering the
path of the review score.

\begin{figure}[h]

{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/example-game-1}

}

\caption{\label{exampleGame} An Example Game in the Sample: Player Count, Price, and Review Score Histories.}\label{fig:example-game}
\end{figure}

Steam is home to more than 25,000 games that differ in their genres,
prices, sales, release dates, frequency of updates, and other
characteristics. Inevitably, an appropriate sample should be selected
for the analysis. \citet{SorokinStevens20} studies the causal effect of
reviews on sales on Steam, and I mirror closely the sample selection
procedure used in that paper. First, Steam has made some significant
changes to its review system in late 2016, and one of the effects was
the removal of the a big number of reviews from the review score
calculation. While it could be an intervention that is worthy of an
independent study, in practice combining the data from before and after
the intervention led to unsound results, so I focus on the two year
period from January 2017 to January 2019, keeping the review system as
stable as possible. In particular, only games that were released in this
time period make it to the sample.

Second, online multiplayer games and games that update frequently are
dropped from the sample, as these are products whose quality is changing
a lot over
time\footnote{Games on Steam have blogs that allow them to share news about updates with the audience. Publishing news about an update is voluntary, so it is possible that some games that continue to update after the release still made it to the sample.}.
Unobserved quality would present a big obstacle to the identification of
the effect of reviews on pricing decisions or sales, because, say, a
game that has just issued a major update might both upgrade to a better
review label (because of the positive reception of the new content) and
give a big discount to rekindle the interest of the players, but the
discounting decision would not be influenced by the review transition.
For the same reasons, I also drop free games and games that are released
in a beta-version (the so called ``Early Access'' program), as these
products are likely to be adding new content, and the update history is
not a perfect way to monitor the updating activity. Finally, I drop few
games with a player count of less than four on their median day, as
these games are simply very small, and the quality of their player count
data is questionable.

\hypertarget{sample-description}{%
\subsection{Sample Description}\label{sample-description}}
